---
title: Landfills in Sub-Saharan Africa A Case Study of Ghana and Kenya
author: Nykol Tudor and Labanya Paul
format: 
  html: 
    toc: true
    toc_depth: 2
    self-contained: true
biliography: bibliography.bib
editor: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

4.  

    ## Results

    The results of the study are presented in this section. The results
    are divided into two parts: the first part presents the results of
    the analysis of the data collected from the landfills in -Ghana and
    and the second part -Kenya.

For Ghana when we did Two way fixed effects model, we found that the
coefficient of the Treatment variable is -0.065, although not
statistically significant.The negative coefficient can be still
interpreted as there is a negative impact on wealth if household is near
the landfill i.e it belongs to the treatment group. But as the result is
not statistically significant, we cannot come to any conclusion.

```         
```

```{r}
library(here)
library(modelsummary)
Reg_tableGhanaTWFE <- readRDS(here("output/Reg_tableGhanaTWFE.rds"))

Reg_tableGhanaTWFE|> modelsummary()
```

```         
```

We also performed only landfill Fixed effect for Ghana(to make it
comparable for Kenya).The coefficient of interest came to be -0.0531,
although again not statistically significant.

```         
```

```{r}
Reg_tableGhana <- readRDS(here("output/Reg_tableGhana.rds"))

Reg_tableGhana|> modelsummary()
```

```         
```

For Kenya as mentioned earlier, we had data for one year 2014. As a
result we could perform only landfill fixed effect model. The
coefficient of interest came to be 0.1559. Although again not
statistically significant, but here it shows a positive impact on wealth
if household is near the landfill i.e it belongs to the treatment group.
This result is quite opposite to what we got for Ghana.

```         
```

```{r}
Reg_tableKenya <- readRDS(here("output/Reg_tableKenya.rds"))

Reg_tableKenya|> modelsummary()
```

## Bibliography

[@here][@modelsummary]
